---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(huxtable)

```

# PDF.extractor

<!-- badges: start -->
<!-- badges: end -->

The goal of PDF.extractor is to automate the reading of PDF lab reports by extracting relevant text into a more readable and searchable dataframe or .csv file.

## Installation

You can install the development version of PDF.extractor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sabrina-xie/PDF.extractor")
```

## Required packages

- pdftools: https://cran.r-project.org/web/packages/pdftools/index.html
- stringr: https://stringr.tidyverse.org
- dplyr: https://dplyr.tidyverse.org

## Examples

To extract a single case narrative, define the filepath of the relevant PDF, which can then be used as an input to case_narrative(). The function will extract each paragraph as a column in a dataframe.

```{r example}
library(PDF.extractor)

# define filepath
filepath <- "~/OneDrive - New York State Office of Information Technology Services/Rscripts/PDF.extractor/inst/R2105522 Summary NYS DEC LCI.pdf"

# run case_narrative()
df <- case_narrative(filepath)

```

```{r, echo=FALSE}
ht <- as_hux(df)
print_md(ht)
```

To extract multiple case narrative, define the filepath of a folder containing only the relevant PDFs, which can then be used as an input to multiple_case_narratives(). The function will extract each paragraph as a column and each sample as a row in a dataframe.

```{r example2}
library(PDF.extractor)

# define filepath
folderpath <- "/Users/sabrinaxie/OneDrive - New York State Office of Information Technology Services/OneDrive_1_12-16-2021"

# run case_narrative()
df <- multiple_case_narratives(folderpath)

```

```{r, echo=FALSE}
ht <- as_hux(df)
print_md(ht)
```
